---
title: "Practical_Machine_Learning_Project_Coursera"
author: "Miss Nassim Bordbar"
date: "Sunday, August 24, 2014"
output: html_document
---


#Method

The code for the method I have used is shown here with comments.
Set working directory
```{r, echo=TRUE}
setwd("C:/Users/nassim.bordbar/Documents/Coursera/ml")
```
Load caret package
```{r echo=TRUE}
library(caret)
```
Reading csv and replacing blank cells with NA
```{r, echo=TRUE}
training <- read.csv("pml-training.csv",na.strings = c("","NA"))
head(training)
validation <- read.csv("pml-testing.csv",na.strings = c("","NA"))
head(validation)
```
Removing columns with NA / non-required columns
```{r, echo=TRUE}
training <- training[,colSums(is.na(training)) == 0]
training <- training[,8:dim(training)[2]]
validation <- validation[,colSums(is.na(validation)) == 0]
validation <- validation[,8:dim(validation)[2]]
```

Creating training and testing dataset
```{r, echo=TRUE}
inTrain <- createDataPartition(y=training$classe,p=0.75, list = FALSE)
testing <- training[-inTrain,]
training <- training[inTrain,]
```

Application of random forests using caret package
```{r, echo=TRUE}
tcr <- trainControl("repeatedcv", number=2, repeats=2, classProbs=TRUE, savePred=T) 
RFFit <- train(classe ~., data=training, method="rf", trControl=tcr)
```

Prediction for own testing dataset
```{r, echo=TRUE}
testing$Prediction <- predict(RFFit, newdata=testing)
```
 
Generation of confusion matrix indicates model is good fit

```{r, echo=TRUE}
cm <- confusionMatrix(data=testing$Prediction, testing$classe)
```


Prediction algorithm applied to predict testing results
```{r, echo=TRUE}
validation$Prediction <- predict(RFFit, newdata=validation)
```

Display results
```{r, echo=TRUE}
validation$Prediction
```